### 2024-02-17 manuscript.tex
Corrected typo in code availability
Corrected typos from reviewer comments

Evolutionary analyses of IDRs reveal widespread signals of conservation

@@

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 high quality alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (\ref{sfig:regions}~Fig). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (\ref{sfig:regions}~Fig). We also searched the database of Pfam domains against the full-length \textit{D. melanogaster} proteins in these alignments and measured their overlap with the disorder and order regions. The results show the disorder set has a clear enrichment in regions with no or only small amounts of overlap relative to the order set, indicating that, compared to structured domains, IDRs are especially resistant to homology-based methods of functional annotation (\ref{sfig:pfam}~Fig).

@@

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available on at \url{https://github.com/marcsingleton/IDR_evolution2023}. The following Python libraries were used: matplotlib~\cite{Hunter2007}, NumPy~\cite{Harris2020}, pandas~\cite{McKinney2010}, SciPy~\cite{Virtanen2020}, and scikit-learn~\cite{Pedregosa2011}. Relevant output files, including the estimated parameters of the substitution, BM, and OU models, are available on Zenodo (DOI: 10.5281/zenodo.10308885). There are no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}

>>>>

Evolutionary analyses of intrinsically disordered regions reveal widespread signals of conservation

@@

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 high quality alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (\ref{sfig:regions}~Fig). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 245 and 105 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (\ref{sfig:regions}~Fig). We also searched the database of Pfam domains against the full-length \textit{D. melanogaster} proteins in these alignments and measured their overlap with the disorder and order regions. The results show the disorder set has a clear enrichment in regions with no or only small amounts of overlap relative to the order set, indicating that, compared to structured domains, IDRs are especially resistant to homology-based methods of functional annotation (\ref{sfig:pfam}~Fig).

@@

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available on GitHub at \url{https://github.com/marcsingleton/IDR_evolution2023}. The following Python libraries were used: matplotlib~\cite{Hunter2007}, NumPy~\cite{Harris2020}, pandas~\cite{McKinney2010}, SciPy~\cite{Virtanen2020}, and scikit-learn~\cite{Pedregosa2011}. Relevant output files, including the estimated parameters of the substitution, BM, and OU models, are available on Zenodo (DOI: 10.5281/zenodo.10308885). There are no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}
